Semantic High-definition Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-10-20 cvpr2018.tex
5th

% Include other packages here, before hyperref.
\usepackage{tabularx} % in the preamble
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\newcommand\VRule[1][\arrayrulewidth]{\vrule width #1}
\usepackage{array,booktabs,arydshln,xcolor} % for widening table line
\usepackage{amsthm}
\usepackage{epstopdf}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{amsthm}
\usepackage{multirow}
\usepackage[algo2e]{algorithm2e}
\usepackage[outercaption]{sidecap}    
\usepackage{float}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{capt-of}% or \usepackage{caption}
\usepackage{booktabs}
\usepackage{varwidth}
% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

@@

%%%%%%%%% TITLE
\title{Semantic Photographic Image Synthesis \\ with a Hierarchically-nested Adversarial Network}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
This paper presents a novel  and effective approach to deal with the challenging task of generating synthetic photographic image conditioned on semantic image descriptions. We leverage the hierarchical deep representations of convolutional layers and introduce deeply-nested adversarial training to constrain the representations to be compositional for multi-scale image generation. To this end, we present a new network architecture, which is symmetric as well as extensile, to push generated images to high resolutions.  We present a functional generative adversarial networks (GANs) training strategy to encourage more effective multimodal (i.e. image and text) information utilization in order to enhance multi-purpose adversary between real and fake. Our method, at the first time, shows a fully end-to-end trainable network that can generate $256{\times}256$ images and is stackable to $512{\times}512$ resolution or higher with arbitrary extensions. With extensive experimental validation on three major datasets, our method sets up a new state of the art to this field.

@@

Generative adversarial networks (GANs) have become the main solution to this task. 
Reed \etal \cite{reed2016generative} takes the first step to address this task through a GAN based framework. But this method only handles image up to $64{\times}64$ resolution and usually is barely to generate vivid object details.
Based on \cite{reed2016generative}, Zhang \etal \cite{han2017stackganan} present a successful approach (StackGAN) by stacking another GAN to generate high quality and compelling $256{\times}256$ images given inputs of low resolution $64{\times}64$ synthetic images. This method needs individual two-stage training, which is relatively not straightforward to be applied. Later on, Dong \etal \cite{dong2017semantic} 
bypasses the difficult of translate vector semantic vector to RGB image and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-renders a arbitrary-style training image according to targeting semantic descriptions. However, the high resolution synthesis ability is still indeterminate. 
Unfortunately, directly training from vector space and synthesize high resolution (e.g. $256{\times}256$) and diverse images is still an open question according to current reported studies.

@@

We have validated our proposed method on three datasets, i.e. CUB birds \cite{}, Oxford-102 flowers \cite{}, and large-scale COCO datasets \cite{}. Extensive experimental results demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts.

\section{Related Work}
There are substantial existing methods investigating better usage of GANs \cite{goodfellow2014generative,radford2015unsupervised} for different applications, such as image synthesis \cite{shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired},  medical imaging \cite{costa2017towards}, etc \cite{ledig2016photo,huang2016stacked}.

Text-to-image synthesis is one of the most challenging tasks requires accurate semantically consistent mapping from a text vector space to a much higher image space.  Reed \etal \cite{reed2016generative} introduces the first method that can generate $64{\times}64$ resolution images, which is similar with DCGAN \cite{}. This method presents a new strategy to image-text matching aware adversarial training. Reed \etal \cite{reed2016learning} propose  generative
adversarial what-where network (GAWWN) to enable "where and what" instructions in text-to-image synthesis, which uses extra information to help generate $128{\times}128$ resolution images. StackGAN \etal \cite{han2017stackgan} propose to a two-stage stacking GAN training approach that is able to generate $256{\times}256$ high resolution vivid images. Recently, \cite{dong2017semantic} proposes to learn a joint embedding of images and text so as to re-render a prototype image according to targeting descriptions.

GANs suffer from optimization difficulties. Wide methods have been proposed to stabilize the training process, for example, one-side label smoothing and discriminator feature matching \cite{salimans2016improved}, training stronger discriminator is beneficial to encourage generators \cite{arjovsky2017wasserstein}. Balancing through a equilibrium enforcing method \cite{berthelot2017began}
Preventing discriminators from forgetting past samples and re-introduces artifacts \cite{shrivastava2016learning}. Increasing the information richness in GANs has been shown very useful \cite{odena2016conditional}.

In term of high resolution image synthesis, cascade networks play an important role.
Denton \etal \cite{denton2015deep} trains a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images, conditioned on random noises and output from last level of the pyramid, to push up output resolution through by-stage refinement. StackGAN also shares similar strategy with LAPGAN. Following this Chen \etal \cite{chen2017photographic} present a cascaded refinement networks to synthesis high-resolution scene from semantic maps. Compared with these strategies that progressively training low- to high-resolution GANs, our method takes advantages of multi-level representation and encourage implicit multi-resolution ensembling, so as to enable end-to-end high-resolution image synthesis.
A recent work from Huang \etal \cite{huang2016stacked}
shows a top-down stack GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method. However, this method need multiple paired  bottom-up discriminators and pre-training. The usage for high-resolution image is difficult (e.g. memory bottleneck) and need verification. More advantages of our method compared with others will be demonstrated in the following.

Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks such as image classification \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified,long2015fully}. DSN \cite{lee2015deeply} proposes deep supervision in hierarchical convolutional layers to increase the discriminativeness of feature representations. Our method is partially inspired by DSN. We introduce accompanying hierarchically-nested adversarial supervision, which enhances and regularizes layer representations to support final high resolution outputs.

@@

\textbf{Generator} The generator is simpled composed by three kinds of modules, termed as $K$-repeat res-blocks, stretching layers, and linear compression layers.
A single res-block in the $K$-repeat res-block is a standard residual block  \cite{he2016identity} containing two convolutional (conv) layers (with batch normalization (BN) \cite{ioffe2015batch} and ReLU). The stretching layer serves to reduce feature map size and dimension. It simply contains an scale-$2$ nearest up-sampling layer followed by a convolutional layer with BN+ReLU. And the linear compression layer is a conv layer followed by a Tan, whose compact design enforces feature maps in conv blocks can linearly represent RGB images at arbitrary scales.
Starting from a $1024{\times}4{\times}4$ embeddings replicated by a $1024$-d text embedding, the generator simples use $M$ $K$-repeat res-blocks connected by $M{-}1$ in-between stretching layers until the feature maps reach to the targeting resolution. We use $K{=}2$ in our method. So for $256{\times}256$ targeting resolution, there are $M{=}6$ $2$-repeat res-blocks and $5$ stretching layers. Such simple and symmetric design makes our generator very effective probably because easier gradient backpropagation. We will verify in experiments. 
With a predefined side-output scales $\{S_i\}$, we apply the compression layer at those scales to produce synthetic images.

\textbf{Discriminator} The discriminator simply contains consecutive stride-2 convolutional layers with BN and LeakyReLU  (the depth changes according to the input size) until the feature map has $512{\times}4{\times}4$ dimension. There two branches are added on top of it for multi-purpose discriminator design (see next section) . One is a direct $4{\times}4$ conv layers to produce a 2-d vector to classify real and fake. Another one first concatenate $128{\times}4{\times}4$ text embedding (replicated from a $128$-d text embedding). Then we use an $1{\times}1$ conv to fuse text and image information; it is critical to guarantee the semantic consistency in the final results. Finally, a $4{\times}4$ conv layer produces a 2-d vector for classification.

@@

\section{Experiments}
In this section, we evaluate the proposed method both qualitatively and quantitatively on three public datasets. We mainly compare to the state-of-the art StackGAN \cite{han2017stackgan}.

\subsection{Evaluation metric}
\subsection{Quantitative and qualitative results}

>>>>

% Include other packages here, before hyperref.
\usepackage{tabularx} % in the preamble
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\newcommand\VRule[1][\arrayrulewidth]{\vrule width #1}
\usepackage{array,booktabs,arydshln,xcolor} % for widening table line
\usepackage{amsthm}
\usepackage{epstopdf}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{amsthm}
\usepackage{multirow}
\usepackage[algo2e]{algorithm2e}
\usepackage[outercaption]{sidecap}    
\usepackage{float}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{capt-of}% or \usepackage{caption}
\usepackage{booktabs}
\usepackage{varwidth}
\usepackage{bm}
% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

@@

%%%%%%%%% TITLE
\title{Semantic High-definition Image Synthesis \\ with a Hierarchically-nested Adversarial Network}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
This paper presents a novel  and effective approach to deal with the challenging task of generating synthetic photographic image conditioned on semantic image descriptions. We leverage the hierarchical deep representations of convolutional layers and introduce deeply-nested adversarial training to regularize the representations to be compositional for multi-scale image generation. To this end, we present a new network architecture, which is symmetric as well as extensile, to push generated images to high resolutions.  We present a functional generative adversarial networks (GANs) training strategy to encourage more effective multimodal (i.e. image and text) information utilization in order to enhance multi-purpose adversary between real and fake distribution. Our method, at the first time, shows a fully end-to-end trainable network that can generate $256{\times}256$ images and is stackable to $512{\times}512$ resolution or higher with arbitrary extensions. With extensive experimental validation on three major datasets, our method sets up a new state of the art to this field.

@@

Generative adversarial networks (GANs) have become the main solution to this task. 
Reed \etal \cite{reed2016generative} takes the first step to address this task through a GAN based framework. But this method only handles image up to $64{\times}64$ resolution and usually is barely to generate vivid object details.
Based on \cite{reed2016generative}, Zhang \etal \cite{han2017stackgan} present a successful approach (StackGAN) by stacking another GAN to generate high quality and compelling $256{\times}256$ images given inputs of low resolution $64{\times}64$ synthetic images. This method needs individual two-stage training, which is relatively not straightforward to be applied. Later on, Dong \etal \cite{dong2017semantic} 
bypasses the difficult of translate vector semantic vector to RGB image and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-renders a arbitrary-style training image according to targeting semantic descriptions. However, the high resolution synthesis ability is still indeterminate. 
Unfortunately, directly training from vector space and synthesize high resolution (e.g. $256{\times}256$) and diverse images is still an open question according to current reported studies.

@@

We have validated our proposed method on three datasets, i.e. CUB birds \cite{}, Oxford-102 flowers \cite{}, and large-scale COCO datasets \cite{}. Extensive experimental results demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts. All source code will be released.

\section{Related Work}
Deep generative models grows wide interests recently, including GANs \cite{goodfellow2014generative}, Variational Auto-encoders (VAE) \cite{kingma2013auto}, etc \cite{oord2016pixel}. 
There are substantial existing methods investigating better usage of GANs for different applications, such as image synthesis \cite{radford2015unsupervised, shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired},  medical imaging \cite{costa2017towards}, etc \cite{ledig2016photo,huang2016stacked}.

Text-to-image synthesis not only requires diverse and high-quality generation but also requires precise semantically consistent mapping in the image space.  Reed \etal \cite{reed2016generative} introduces the first method that can generate $64{\times}64$ resolution images, which is similar with DCGAN \cite{}. This method presents a new strategy to image-text matching aware adversarial training. Reed \etal \cite{reed2016learning} propose  generative
adversarial what-where network (GAWWN) to enable "where and what" instructions in text-to-image synthesis, which uses extra information to help generate $128{\times}128$ resolution images. StackGAN \etal \cite{han2017stackgan} propose to a two-stage stacking GAN training approach that is able to generate $256{\times}256$ high resolution vivid images. Recently, \cite{dong2017semantic} proposes to learn a joint embedding of images and text so as to re-render a prototype image according to targeting descriptions.

Learning a continuous mapping from low-dimensional embeddings to complex real data distribution is a long-standing problem. Although GANs have made significant progressive, there are still many not well-solved difficulties, e.g. training instability. Wide methods have been proposed to stabilize the training process, through various training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, auxiliary regularization from outside knowledge (e.g. labels, imagenet CNNs , etc) \cite{dosovitskiy2016generating,ledig2016photo}. Moreover, such difficulties grow significantly when targeting image resolution increases.

%for example, label smoothing and discriminator feature matching \cite{salimans2016improved, }, training stronger discriminator is beneficial to encourage generators \cite{arjovsky2017wasserstein}. Balancing through a equilibrium enforcing method \cite{berthelot2017began}
%Preventing discriminators from forgetting past samples and re-introduces artifacts \cite{shrivastava2016learning}. Increasing the information richness in GANs has been shown very useful \cite{odena2016conditional}.

To synthesize high resolution image, cascade networks play an important role to decompose original difficult tasks to multiple subtasks.
Denton \etal \cite{denton2015deep} trains a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images, conditioned on random noises and output from last level of the pyramid, to push up output resolution through by-stage refinement. StackGAN also shares similar strategy with LAPGAN. Following this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement networks to synthesis high-resolution scene from semantic maps. 
Huang \etal \cite{huang2016stacked}
shows a top-down stack GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method. However, this method need multiple symmetric  bottom-up discriminators and pre-training of discriminators. The usage for high-resolution image is unclear \cite{han2017stackgan}. Compared with these strategies that progressively training low- to high-resolution GANs, our method takes advantages of multi-level representation and encourage implicit multi-resolution ensembling, so as to enable end-to-end high-resolution image synthesis.

%More advantages of our method compared with others will be demonstrated in the following.

Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks such as image classification \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified,long2015fully}. DSN \cite{lee2015deeply} proposes deep supervision in hierarchical convolutional layers to increase the discriminativeness of feature representations. 
Our method is partially inspired by supervised CNNs with deep supervision \cite{lee2015deeply,xie2015holistically}. We introduce accompanying hierarchically-nested adversarial supervision, with a goal to enhance and regularizes layer representations to support final high resolution outputs.

@@

\textbf{Generator} The generator is simpled composed by three kinds of modules, termed as $K$-repeat res-blocks, stretching layers, and linear compression layers.
A single res-block in the $K$-repeat res-block is a standard residual block  \cite{he2016identity} containing two convolutional (conv) layers (with batch normalization (BN) \cite{ioffe2015batch} and ReLU). The stretching layer serves to reduce feature map size and dimension. It simply contains an scale-$2$ nearest up-sampling layer followed by a convolutional layer with BN+ReLU. And the linear compression layer is a conv layer followed by a Tan, whose compact design enforces feature maps in conv blocks can linearly represent RGB images at arbitrary scales.
Starting from a $1024{\times}4{\times}4$ embeddings replicated by a $1024$-d text embedding, the generator simples use $M$ $K$-repeat res-blocks connected by $M{-}1$ in-between stretching layers until the feature maps reach to the targeting resolution. So for $256{\times}256$ targeting resolution with $K{=}1$, there are $M{=}6$ $1$-repeat res-blocks and $5$ stretching layers. Such simple and symmetric design makes our generator helpful for gradient flows. We will verify in experiments. 
With a predefined side-output scales $\{S_i\}$, we apply the compression layer at those scales to produce synthetic images.

\textbf{Discriminator} The discriminator simply contains consecutive stride-2 conv layers with BN and LeakyReLU \cite{} (the depth changes according to the input size) until the feature map has $512{\times}4{\times}4$ dimension. There two branches are added on top of it for multi-purpose discriminator design (see next section) . One is a direct $4{\times}4$ conv layers to produce a 2-d vector to classify real and fake. Another one first concatenate $128{\times}4{\times}4$ text embedding (replicated from a $128$-d text embedding). Then we use an $1{\times}1$ conv to fuse text and image information; it is critical to guarantee the semantic consistency in the final results. Finally, a $4{\times}4$ conv layer produces a 2-d vector.

@@

\section{Experiments}
In this section, we evaluate the proposed method both qualitatively and quantitatively on three public datasets. StackGAN \cite{han2017stackgan} generates synthetic images up to  $256{\times}256$ resolution. We show that our method can generates images up to  $512{\times}512$. We denote our method as HDGAN, referring as High-definition results as well as the design of hierarchically-nested discriminators.

%We mainly compare to the state-of-the art StackGAN \cite{han2017stackgan} for text-to-image synthesis and demonstrate substantially improvement.

\subsection{Evaluation metric}

\begin{table}[t] % retrieval
	\begin{center}
		\begin{tabularx}{.477\textwidth}{c|ccc}
			\specialrule{1.5pt}{0pt}{0pt}  
			\multirow{2}{*}{Method}	& \multicolumn{3}{c}{Dataset}	\\ \cline{2-4}
							 		&	 CUB		&	Oxford  & COCO		     \\ \hline
			GAN-INT-CLS 	&	$2.88{\pm}.04$		& 	$2.66{\pm}.03$		& $7.88{\pm}.07$	 \\
			GAWWN 	  &		$3.60{\pm}.07$		&     -      &          - \\ 
			StackGAN     &		$3.70{\pm}.04$	&	 $3.20{\pm}.01$			&  $8.45{\pm}.03$		\\ \hline
		%	StackGAN$^\star$     &		$3.89{\pm}.05$	&	 $3.16{\pm}.01$			&  $8.45{\pm}.03$		\\ \hline
			HDGAN 		&	$\bm{4.01{\pm}.04}$	&	$ \bm{3.45{\pm}.07}$			&  -  \\ \hline
		\end{tabularx} \vspace{-.4cm}
	\end{center}
	\caption{The inception-score evaluation on three datasets. The higher score reflects more meaningful synthetic images and higher diversity. The proposed HDGAN outperforms others significantly.} \label{table:score}
\end{table}

\subsection{Comparative Results}
We compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, and  StackGAN \cite{han2017stackgan}. StackGAN is currently the state of the art method.

Table \ref{table:score} shows the quantitative evaluation. HDGAN achieves significantly improvement compared to other methods. For example, HDGAN improves GAN-INT-CLS by ${\sim}30.1\%$  and ${\sim}8.4\%$ on CUB.

   Specifically, compared with StackGAN, HDGAN improves
